---
title: "Teams and results"
execute: 
  warning: false
---

```{r, include=FALSE}
library(tidyverse)
library(rvest)
library(polite)
library(tidyr)
library(kableExtra)
library(DT)

# Load in stage data

Stage_1 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-1/result/result")
Sprint <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-1-points")
Stage_2 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-2/result/result")
Stage_3 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-3/result/result")
Stage_4 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-4/result/result")
Stage_5 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-5/result/result")
Stage_6 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-6/result/result")
Stage_7 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-7/result/result")
Stage_8 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-8/result/result")
Stage_9 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-9/result/result")
Stage_10 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-10/result/result")
Stage_11 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-11/result/result")
Stage_12 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-12/result/result")
Stage_13 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-13/result/result")
Stage_14 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-14/result/result")
Stage_15 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-15/result/result")
Stage_16 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-16/result/result")
Stage_17 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-17/result/result")
Stage_18 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-18/result/result")
Stage_19 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-19/result/result")
Stage_20 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-20/result/result")
Stage_21 <- read_html("https://www.procyclingstats.com/race/tour-de-france/2024/stage-21/result/result")

```

```{r, include=FALSE}
# Get results

stage_1_results <- Stage_1 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 1,
         `Most combative` = if_else(BIB == 187, "YES", "NO"))

stage_2_results <- Stage_2 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 2,
         Rnk = as.factor(Rnk),
         `Most combative` = if_else(BIB == 202, "YES", "NO"))

stage_3_results <- Stage_3 %>%
 html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 3,
         Rnk = as.character(Rnk),
         `Most combative` = if_else(BIB == 215, "YES", "NO"))

stage_4_results <- Stage_4 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 4,
          Rnk = as.character(Rnk),
         `Most combative` = if_else(BIB == 155, "YES", "NO"))

stage_5_results <- Stage_5 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 5,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = if_else(BIB == 98, "YES", "NO"))

stage_6_results <- Stage_6 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 6,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = if_else(BIB == 45, "YES", "NO"))

stage_7_results <- Stage_7 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 7,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = "NO")

stage_8_results <- Stage_8 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 8,
         Rnk = recode(Rnk, DNF = "NA"),
         Rnk = as.factor(Rnk),
         `Most combative` = if_else(BIB == 202, "YES", "NO"))

stage_9_results <- Stage_9 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 9,
         #Rnk = recode(Rnk, DNF = "NA"),
         Rnk = as.factor(Rnk),
         `Most combative` = if_else(BIB == 47, "YES", "NO"))

stage_10_results <- Stage_10 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 10,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = if_else(BIB == 173, "YES", "NO"))

stage_11_results <- Stage_11 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 11,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = if_else(BIB == 11, "YES", "NO"))

stage_12_results <- Stage_12 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 12,
         Rnk = recode(Rnk, DNF = "NA"),
         Rnk = as.factor(Rnk),
         `Most combative` = if_else(BIB == 97, "YES", "NO"))

stage_13_results <- Stage_13 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 13,
         Rnk = recode(Rnk, DNF = "NA"),
         Rnk = as.factor(Rnk),
         `Most combative` = if_else(BIB == 201, "YES", "NO"))

stage_14_results <- Stage_14 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 14,
         Rnk = recode(Rnk, DNF = "NA"),
         Rnk = as.factor(Rnk),
         `Most combative` = if_else(BIB == 115, "YES", "NO"))

stage_15_results <- Stage_15 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 15,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = if_else(BIB == 111, "YES", "NO"))

stage_16_results <- Stage_16 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 16,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = "214")

stage_17_results <- Stage_17 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 17,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = if_else(BIB == 93, "YES", "NO"))

stage_18_results <- Stage_18 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 18,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = if_else(BIB == 204, "YES", "NO"))

stage_19_results <- Stage_19 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 19,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = if_else(BIB == 111, "YES", "NO"))

stage_20_results <- Stage_20 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 20,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = if_else(BIB == 151, "YES", "NO"))

stage_21_results <- Stage_21 %>%
  html_node("table") %>% 
  html_table() %>% 
  as_tibble(.name_repair = "unique") %>% 
  select(Rnk, GC, BIB, Rider) %>% 
  mutate(Stage = 21,
         Rnk = as.factor(Rnk),
         Rnk = recode(Rnk, DNF = "NA"),
         `Most combative` = "NO")

Stage_list <- list(stage_1_results, stage_2_results, stage_3_results, stage_4_results,
                   stage_5_results, stage_6_results, stage_7_results, stage_8_results, 
                   stage_9_results, stage_10_results, stage_11_results, stage_12_results, stage_13_results, stage_14_results, stage_15_results, stage_16_results, stage_17_results, stage_18_results, stage_19_results, stage_20_results, stage_21_results)
                
```

# 2024 Lineups

$~$

Our lineups for 2024. 12 month PCS rankings are shown in brackets next to the riders. *Pogacar has accumulated 3833 points since the beginning of last year's tour. Only four other riders get to even half this total.

```{r, echo=FALSE}
Teams <- 
  tibble(`Rider type` = c("General", "General", "General", "General", "Domestique", "Sprinter", "Sub 1", "Sub 2", "12 month PCS points"),
         Zing = c("Pogačar Tadej (1)*", "Cavendish Mark (330)", "Martinez Lenny (32)", "Bilbao Pello (DNF)", "Almeida Joao (26)", "Pedersen Mads (DNF)", "Landa Mikel (Subbed in)", "Onley Oscar (Subbed in)", "10,968"),
         Bergs = c("Vingegaard Jonas (5)", "Gaudu David (94)", "Healy Ben (105)", "Bernal Egan (59)", "Powless Neilson (185)", "Jakobsen Fabio (DNF)", "Mas Enric (Subbed in)", "Fuglsang Jakob (470)", "5,514"),
         Falcs = c("Evenepoel Remco (3)", "Skujins Toms (74)", "Pidcock Tom (DNF)", "Mohorič Matej (25)", "Van Der Poel Mathieu (9)", "Cort Magnus (219)", "Girmay Biniam (Subbed in)", "Thomas Geraint (DNF)", "8,243"),
         Haz = c("Roglic Primoz (DNF)", "Buitrago Santiago (75)", "Williams Stephen (36)", "Yates Simon (23)", "Van aert Wout (10)", "De Lie Arnaud (14)", "Van Gils Maxim (Subbed in)", "Haig Jack (325)", "8,876"),
         Ben = c("Rodriguez Carlos (16)", "Ayuso Juan (DNF)", "Ciccone Giulio (133)", "Matthews Michael (69)", "Bettiol Alberto (DNF)", "Philipsen Jasper (2)", "Carapaz Richard (Subbed in)", "Martin Guillaume (Subbed in)", "8,768"),
         Willo = c("Yates Adam (7)", "Gee Derek (194)", "Vlasov Aleksandr (DNF)", "Hindley Jai (45)", "Jorgenson Matteo (22)", "Groenewegen Dylan (34)", "Gall Felix (Subbed in)", "Bennett Sam (89)", "8,220"),
         `Free agents` = c("Gregoire Romain (76)", "Demare Arnaud (137)", "Campenaerts Victor (302)",
                           "Lazkano Oier (131)", "Kragh Andersen Soren (DNF)", "Bauhaus Phil (101)",
                           "Vermeersch Gianni (Subbed in)", "NA", "2,682")) 

# For the standings

#startlist <- read_csv("Riders.csv") #%>%
  #mutate(`Sub activated` = case_when(BIB == 8 ~ "6",
   #                                  BIB == 151 ~ "9",
    #                                 BIB == 131 ~ "9",
     #                                BIB == 25 ~ "15",
      #                               BIB != c(8, 11, 151, 131) ~ "NO"))

  


# Who has who?

#Teams %>% 
 # kbl() %>% 
  #kable_minimal() %>% 
 # column_spec(8, background = spec_color(data$`DIFFERENCE RANK`, option = "A", begin = 0.6, end = 0.95))
  
Teams %>%
 # mutate(Zing = cell_spec(Zing, strikeout = ifelse(Zing == "Pedersen Mads (4)", TRUE, FALSE))) %>%  
 #        Falcs = cell_spec(Falcs, "html", strikeout = ifelse(Falcs == "Carapaz Richard (73)" | Falcs == "Cavendish Mark (167)", TRUE, FALSE)),
  #       Willo = cell_spec(Willo, "html", strikeout = ifelse(Willo == "Jakobsen Fabio (51)", TRUE, FALSE)), 
   #      Zing = cell_spec(Zing, "html", strikeout = ifelse(Zing == "Bardet Romain (22)", TRUE, FALSE)),
    #     Haz = cell_spec(Haz, "html", strikeout = ifelse(Haz == "Ewan Caleb (49)", TRUE, FALSE))) %>% 
  knitr::kable(escape = F, format="markdown") %>% 
  kable_styling() %>% 
  #cell_spec(2, strikeout = ifelse(Zing == "Pedersen Mads (4)", TRUE, FALSE)) %>%
  #row_spec(5, color = "black", background = "#89c0b6") %>% 
  row_spec(7:8, color = "white", background = "#A7D3D4") %>% 
  column_spec(1, bold = TRUE)
  
```

$~$

# Final standings

$~$

```{r, echo=FALSE}
  
Stage_Scoring <- function(stage_data){
  stage_data %>%
  mutate(stage_points = recode(Rnk, "1" = 10, "2" = 6, "3" = 4, "4" = 2, "5" = 1, .default = 0),
         GC_points = recode(GC, "1" = 25, "2" = 22, "3" = 20,
                            "4" = 18, "5" = 16, "6" = 14, "7" = 14,
                            "8" = 12, "9" = 10, "10" = 10, "11" = 8,
                            "12" = 8, "13" = 6, "14" = 6, "15" = 6, .default = 0),
         `Most combative points` = if_else(`Most combative` == "YES", 10, 0))
}

Total_score <- map_dfr(Stage_list, Stage_Scoring) 

Total_score_tidy <- Total_score %>% 
  group_by(BIB) %>% 
  mutate(Total_stage_points = sum(stage_points, na.rm = TRUE),
         Total_most_combative_points = sum(`Most combative points`, na.rm = TRUE)) #%>% 
  #distinct(BIB, .keep_all = TRUE)

a <- 
  Total_score_tidy %>%
  distinct(BIB, .keep_all = TRUE) %>% 
  select(Rider, BIB, Total_stage_points, Total_most_combative_points)

b <-
  Total_score %>% 
  filter(Stage == max(Stage)) %>%
  select(GC, BIB, GC_points)

Results_complete <- 
  left_join(a, b) %>%
  mutate(Directeur = case_when(
    BIB == 81 | BIB == 64 | BIB == 131 | BIB == 21 | BIB == 8 | BIB == 121 | BIB == 126 ~ "Haz",
    BIB == 1| BIB == 91| BIB == 115| BIB == 32| BIB == 116 | BIB == 185 | BIB == 151 ~ "Bergs",
    BIB == 71| BIB == 46| BIB == 36| BIB == 66| BIB == 101 | BIB == 201 | BIB == 172 ~ "Falcs",
    BIB == 11| BIB == 191| BIB == 96| BIB == 61| BIB == 12 | BIB == 45 | BIB == 74 | BIB == 186 ~ "Zing",
    BIB == 31 | BIB == 13| BIB == 41| BIB == 26| BIB == 112 | BIB == 106 | BIB == 111 | BIB == 141 ~ "Ben",
    BIB == 18| BIB == 135 | BIB == 88 | BIB == 84 | BIB == 3 | BIB == 23 | BIB == 51 ~ "Willo",
    BIB == 93| BIB == 164 | BIB == 123 | BIB == 155 | BIB == 104 | BIB == 63 | BIB == 108 ~ "Free agents",
    .default = "Not selected"
  )) %>% 
  # add the jersey wearing points
  mutate(Yellow_wearer_points = case_when(BIB == 181 | BIB == 11 | BIB == 111  ~ "10",
                                          .default = "0"),
         Green_wearer_points = case_when(BIB == 187 | BIB == 202 | BIB == 172 ~ "5",
                                         .default = "0"),
         White_wearer_points = case_when(BIB == 187 | BIB == 71 ~ "5",
                                         .default = "0"),
         Polka_wearer_points = case_when(BIB == 202 | BIB == 11 | BIB == 111 ~ "5",
                                         .default = "0"),
         Domestique_points = case_when(BIB == 3 ~ "20", # 14 + 6
                                       BIB == 8 ~ "17", # 11 + 6
                                       BIB == 12 ~ "25", # 17 + 8
                                       BIB == 116 ~ "4",
                                       BIB == 101 | BIB == 104 ~ "13",
                                         .default = "0")) %>% 
  ungroup() %>% 
  mutate(across(8:12, ~ as.numeric(.x))) %>% 
  mutate(GC_points = replace_na(GC_points, 0),
         #GC = replace_na(GC, "DNF"), 
         Jersey_points = Yellow_wearer_points + Green_wearer_points + White_wearer_points + 
           Polka_wearer_points,
         `Green points` = recode(BIB, "172" = 10, "106" = 8, "143" = 6, .default = 0),
         `White points` = recode(BIB, "71" = 10, "31" = 8, "3" = 6, .default = 0),
         `Mountain points` = recode(BIB, "111" = 10, "11" = 6, "1" = 4, .default = 0),
          Final_score = Total_stage_points + GC_points + Total_most_combative_points + 
           Yellow_wearer_points + Green_wearer_points + White_wearer_points + 
           Polka_wearer_points + `Green points` + `Mountain points` + `White points` + Domestique_points) %>% 
  arrange(-Final_score) %>% 
  select(Rider, BIB, Directeur, GC, Total_stage_points, Total_most_combative_points, GC_points, Jersey_points, Domestique_points, `Green points`, `White points`, `Mountain points`, Final_score)
  

Team_rankings <-
  Results_complete %>%
  select(-c(Rider, BIB)) %>% 
  #filter(Sub == "NO" | `Sub activated` != "NO") %>% # fix this so sub activates
  group_by(Directeur) %>% 
  mutate(`Provisional score` = sum(Final_score),
         `Confirmed points` = sum(Total_stage_points) + sum(Total_most_combative_points) +
           sum(Jersey_points) + sum(Domestique_points)) %>% 
  arrange(-`Provisional score`) %>% 
  distinct(Directeur, .keep_all = TRUE) %>% 
  select(Directeur, `Confirmed points`, `Provisional score`) %>%
  mutate(`Confirmed points` = case_when(Directeur == "Falcs" ~ `Confirmed points` - 49,
                                        Directeur == "Ben" ~ `Confirmed points` - 10,
                                        Directeur == "Haz" ~ `Confirmed points` - 1,
                                        .default = `Confirmed points`),
         `Provisional score` = case_when(Directeur == "Falcs" ~ `Provisional score` - 49,
                                        Directeur == "Ben" ~ `Provisional score` - 10,
                                        Directeur == "Haz" ~ `Provisional score` - 1,
                                        .default = `Provisional score`)) %>% 
  filter(Directeur  != "Not selected")

Rider_rankings <-
  Results_complete %>% 
  arrange(-Final_score) %>% 
  rename(`Final score` = Final_score) %>% 
  rename(`Directeur sportif` = Directeur,
         `Cumulative stage points` = Total_stage_points,
         `Cumulative most combative points` = Total_most_combative_points,
         `GC points` = GC_points)# %>% 
  #mutate(`Green points` = recode(BIB, "19" = 10, "161" = 8, "11" = 6, .default = 0),
  #       `Mountain points` = recode(BIB, "46" = 10, "184" = 6, "118" = 4, .default = 0),
    #     `Final score` = `Provisional score` + `Green points` + `Mountain points`) 

#Break_kms <- tibble(
 # Directeur = c("Haz", "Bergs", "Falcs", "Zing", "Stiff", "Willo"),
  #Break_kms = c(2481, 922, 847, 738, 1431, 833)) %>% 
  #mutate(`Break points` = round(Break_kms / 50, 0))

```


```{r, echo=FALSE}
#Break_kms %>% 
 # rename(`Breakaway kms` = Break_kms) %>% 
  #arrange(-`Breakaway kms`) %>% 
  #tibble(#Sub_penalty = c(0, 0, 0, 0, -20, 0),
       #  Green_points = c(14, 0, 10, 0, 0, 0),
        # Mountain_points = c(4, 10, 0, 0, 0, 0)) %>% 
 # mutate(`Confirmed points` = `Confirmed points` #+ Sub_penalty,
  #       `Final score` = `Provisional score` + Sub_penalty + Green_points + Mountain_points) %>% 
  #select(`Directeur sportif`, `Final score`, Green_points, Mountain_points) %>% 
  #arrange(-`Final score`) %>% 
  #kable() %>% 
  #kable_styling()
```


```{r, echo=FALSE}
Team_rankings %>% 
  rename(`Final score` = `Provisional score`) %>% 
  select(Directeur, `Final score`) %>% 
  #left_join(Break_kms %>% select(Directeur, `Break points`)) %>%
  #mutate(`Final score` = `Final score` + `Break points`) %>% 
  arrange(-`Final score`) %>% 
  #tibble(#Sub_penalty = c(0, 0, 0, 0, -20, 0),
       #  Green_points = c(14, 0, 10, 0, 0, 0),
        # Mountain_points = c(4, 10, 0, 0, 0, 0)) %>% 
 # mutate(`Confirmed points` = `Confirmed points` #+ Sub_penalty,
  #       `Final score` = `Provisional score` + Sub_penalty + Green_points + Mountain_points) %>% 
  #select(`Directeur sportif`, `Final score`, Green_points, Mountain_points) %>% 
  #arrange(-`Final score`) %>% 
  kable() %>% 
  kable_styling()
```

# Rider rankings

```{r, echo=FALSE}


# Create a function to build HTML searchable tables

my_data_table <- function(df){
  datatable(
    df, rownames=FALSE,
    autoHideNavigation = TRUE,
    extensions = c("Scroller",  "Buttons"),
    options = list(
      dom = 'Bfrtip',
      deferRender=TRUE,
      scrollX=TRUE, scrollY=600,
      scrollCollapse=TRUE,
      buttons =
        list('pageLength', 'colvis', 'csv', list(
          extend = 'pdf',
          pageSize = 'A4',
          orientation = 'landscape',
          filename = 'tour_data')),
      pageLength = 100
    )
  )
}


Rider_rankings %>% 
                select(Rider, `Directeur sportif`, `Final score`,
                       `GC points`, `Green points`, `White points`, `Mountain points`, `Cumulative stage points`, `Cumulative most combative points`, Jersey_points, Domestique_points) %>% 
  my_data_table()
```

## Stage results

### Stage 1

```{r, echo=FALSE}
  
Stage_Scoring(stage_1_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 2

```{r, echo=FALSE}
  
Stage_Scoring(stage_2_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 3

```{r, echo=FALSE}
  
Stage_Scoring(stage_3_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 4

```{r, echo=FALSE}
  
Stage_Scoring(stage_4_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 5

```{r, echo=FALSE}
  
Stage_Scoring(stage_5_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 6

```{r, echo=FALSE}
  
Stage_Scoring(stage_6_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 7

```{r, echo=FALSE}
  
Stage_Scoring(stage_7_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 8

```{r, echo=FALSE}
  
Stage_Scoring(stage_8_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 9

```{r, echo=FALSE}
  
Stage_Scoring(stage_9_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 10

```{r, echo=FALSE}
  
Stage_Scoring(stage_10_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 11

```{r, echo=FALSE}
  
Stage_Scoring(stage_11_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 12

```{r, echo=FALSE}
  
Stage_Scoring(stage_12_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 13

```{r, echo=FALSE}
  
Stage_Scoring(stage_13_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 14

```{r, echo=FALSE}
  
Stage_Scoring(stage_14_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 15

```{r, echo=FALSE}
  
Stage_Scoring(stage_15_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 16

```{r, echo=FALSE}
  
Stage_Scoring(stage_16_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 17

```{r, echo=FALSE}
  
Stage_Scoring(stage_17_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 18

```{r, echo=FALSE}
  
Stage_Scoring(stage_18_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 19

```{r, echo=FALSE}
  
Stage_Scoring(stage_19_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 20

```{r, echo=FALSE}
  
Stage_Scoring(stage_20_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```

### Stage 21

```{r, echo=FALSE}
  
Stage_Scoring(stage_21_results) %>%
        rename(`Stage result` = Rnk,
               `Stage points` = stage_points) %>% 
                select(Rider, `Stage result`, `Stage points`) %>% 
  kable() %>% 
  kable_styling() %>% 
   scroll_box(width = "800px", height = "800px")
  
```
